\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2023-01-01 Latex/paper.tex
# new figures and some modifications in the examples

\subsection{CMSs}
We will define the swap rate from $T_a$ to $T_b$ at time $t$
\begin{equation*}
S_{a,b}(t) = \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,T_a,T_b)}
\end{equation*}
where
\begin{align*}
01(t,T_a,T_b) = \sum_{j=1}^{n_f} \delta_{t^{f}_{i-1}, t^{f}_i} P_{ois}(t,t^{f}_{j}) \\
T_a=T^{E}_0 < T^{E}_i< \cdots < T^{E}_{n_E}=T_b \quad i=0,\cdots,n_E&  \\
T_a=T^{f}_0 < T^{f}_j< \cdots < T^{f}_{n_f}=T_b \quad j=0,\cdots,n_f&
\end{align*}
The same way, let us define
\begin{equation*}
S^{ois}_{a,b}(t) = \frac{P_{ois}(t,T^{E}_a) - P_{ois}(t,T^{E}_b)}{01(t,T_a,T_b)}. 
\end{equation*}

We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. Then, the present value of this flow under the differents measure $\mathbb{Q}^{T_a}$,$\mathbb{Q}^{01(a,b)}$ and $\mathbb{Q}^{T_p}$ respectivaly is 
\begin{align}\label{cms_expedted_value}
P_{ois}(0,T_a)\mathbb{E}^{\mathbb{Q}^{T_{a}}}\left(S_{a,b}(T_a) P_{ois}(T_a,T_p) \right) &= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) \frac{P_{ois}(T_a,T_p)}{01(T_a,T_a,T_b) }\right) \nonumber \\
&= 01(0,T_a,T_b) \mathbb{E}^{\mathbb{Q}^{01(a,b)}}\left(S_{a,b}(T_a) M(T_a,T_p)\right) \\
&=P_{ois}(0,T_p)\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right)
\end{align}
where $M(t, T_p)= \frac{P_{ois}(t,T_p) }{01(t,T_a,T_b)} $. From the definition of $S_{a,b}(t)$ and $S^{ois}_{a,b}(t)$, we have that both are martingale under the measure $\mathbb{Q}^{01(a,b)}$. Therefore, we will define the convexity adjustment for CMS the next  way
\begin{equation*}
CA_{cms}(T_0,T_p) = S_{a,b}(0) - \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right). 
\end{equation*}
We will follow the same strategy that in the last examples. From Clark-Ocone formula we have that
\begin{equation*}
S_{a,b}(T_a) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s 
\end{equation*} 
Therefore, if we take $\mathbb{E}^{01(a,b)}$ and we use the Girsanov theorem  in the last expression, we get 
\begin{equation*}
S_{a,b}(0) = \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + M(0,T_p) \mathbb{E}^{T_p}\left( \frac{1}{M(T_a,T_p)} \int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) dW^{T_p}_s \right)
\end{equation*}
Now, if we use that the Skorohod integral is the adjoint operator of the Malliavin derivative, we have that
\begin{align*}
S_{a,b}(0) &= \mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + M(0,T_p) \mathbb{E}^{T_p}\left(\int_{0}^{T_a} D_s \left(\frac{1}{M(T_a,T_p)} \right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right) \\
&=\mathbb{E}^{\mathbb{Q}^{T_p}}\left(S_{a,b}(T_a)\right) + M(0,T_p) \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\frac{1}{M(T_a,T_p)} \right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
\end{align*}
Then we have the next expression for the convexity adjustment
\begin{equation*}
CA_{cms}(T_0,T_p) = - \frac{01(0,T_a,T_b)}{P_{ois}(0,T_p)} \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s \left(\frac{1}{M(T_a,T_p)}\right)\right) \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(D_s S_{a,b}(T_a)\right) ds  \right).
\end{equation*}
Now, if we do a freeze of $\partial_x M(t,T_p)$ and $\partial_x S_{a,b}(t)$, then we can do the next approximation for $CA_{ois}(T_0,T_p)$
\begin{align*}
CA_{cms}(T_0,T_p) &=  - M(0,T_p) \mathbb{E}^{T_p}\left(\int_{0}^{T_a} \mathbb{E}^{T_p}_s \left(\partial_x \left(\frac{1}{M(T_a,T_p)}\right) D_s x_{T_a}\right) \mathbb{E}^{T_p}_s \left(\partial_x S_{a,b}(T_a)D_s x_{T_a} \right) ds \right) \\
& \approx c \frac{ \partial_x M(T_a,T_p, x_0, y_0)}{M(T_a,T_p, x_0, y_0)}  \partial_x S^{ois}_{a,b}(T_a,x_0,y_0) \mathbb{E}^{\mathbb{Q}^{T_p}}\left(\int_{0}^{T_a} \left(D_s x_{T_a} \right)^{2} ds \right).
\end{align*}
with $c = \frac{S_{a,b}(0)}{S^{ois}_{a,b}(0)}$. Now, if we use (\ref{approximation_D_s_x_t}) we can estimate  
$
 \mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\left(D_s x_{T_a} \right)^{2}\right)
$
the next way 
\begin{align*} 
\mathbb{E}_s^{\mathbb{Q}^{T_p}}\left(\left(D_s x_{T_a} \right)^{2}\right) &\approx \exp\left(-2 \int_{s}^{T_a}k_u du \right) \eta^{2}(s,\bar{x}_0,\bar{y}_{T_a}) \\
& \cdot \exp\left(\int_{s}^{T_a} \left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2} - 2 \exp\left(-\int_{s}^{T_a}k_u du\right) \partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p)) \right) du
\end{align*}
Therefore, we have that
\begin{align*}
CA_{cms}(T_0,T_p) &\approx 
\end{align*}

\begin{example}
In the case of a Hull-White model, we showed  in (\ref{example_convexity_hw_ois}) that 
$$
\eta(t,x_t, y_t) = \sigma\exp(-kt)
$$
and
$$
D_s x_{T_a} = \sigma \exp(-(T_a - s))
$$
and therefore, we have that
\begin{equation*}
\mathbb{E}^{\mathbb{Q}^{T_p}}\left(\int_{0}^{T_a}(D_s x_{T_a})^{2} ds \right) = \sigma^{2} \frac{1 - \exp(-2kT_a)}{2k}.
\end{equation*}

In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method
\end{example}

\section*{Appendix}
\appendix
\renewcommand{\thesection}{\Alph{section}.\arabic{section}}
\section{Approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$}
\label{expected_forward_measure_malliavin_derivative_x_t}
From (\ref{short_rate_cheyette}) is easy to show that
\begin{equation*}
x_{T_a} = \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) y_u du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}}  
\end{equation*}
In order to get an approximation for $D_sX_{T_a}$ we must to avoid the recurrence in the Malliavin derivative of $X_{T_a}$. Follow, the ideas of Piterbarg Volume II, we can approximate $y_t$ the next way
\begin{equation*}
y_t \approx \int_{0}^{t} \exp\left(-2\int_{u}^{t} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du
\end{equation*}
Therefore, if we define $\bar{y}(t)= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0)$, we have that
\begin{equation*}
X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}  
\end{equation*}
With initial condition  $\bar{x}_{0}$ is such that $S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) = S_{a,b}(0)$ (see Piterbarg Volume II). Now, we must remember that by Girsanov's theorem we have that 
\begin{equation*}
dW^{\mathbb{Q}^{T_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,T_p) dt 
\end{equation*}
where $\bar{\nu}(t,T_p) = \int_{t}^{T_p} \eta(s,\bar{x}_s,\bar{y}_s) ds $. Then, we have the next approximation of $\bar{x}_{T_a}$
\begin{align*}
X_{T_a} &\approx \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}_s ds - \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{\nu}(s, T_p) \eta(s,\bar{x}_s,\bar{y}_s) ds +  \\
&+ \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \partial_x \eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}}  
\end{align*} 
Therefore, if we taj¡ke the Malliavin derivative of $\bar{X}_{T_a}$ we get
\begin{equation}\label{approximation_D_s_x_t}
D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
\end{equation}
where
\begin{align*}
\bar{M}(s,T_a) &= \exp\left(-\int_{s}^{T_a} \left( \frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p))\right) du \right) \\ 
&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}}_u \right)
\end{align*}
With $\beta(u,T_a,x,y) = \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x \eta(u,x,y)$. Therefore, if we use the last equalities, we get the next approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$

@@

>>>>

\subsection{CMSs}
We will define the swap rate from $T_a$ to $T_b$ at time $t$
\begin{equation*}
S_{a,b}(t) = \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,T_a,T_b)}
\end{equation*}
where
\begin{align*}
01(t,T_a,T_b) = \sum_{j=1}^{n_f} \delta_{t^{f}_{i-1}, t^{f}_i} P_{ois}(t,t^{f}_{j}) \\
T_a=T^{E}_0 < T^{E}_i< \cdots < T^{E}_{n_E}=T_b \quad i=0,\cdots,n_E&  \\
T_a=T^{f}_0 < T^{f}_j< \cdots < T^{f}_{n_f}=T_b \quad j=0,\cdots,n_f&
\end{align*}
The same way, let us define
\begin{equation*}
S^{ois}_{a,b}(t) = \frac{P_{ois}(t,T^{E}_a) - P_{ois}(t,T^{E}_b)}{01(t,T_a,T_b)}. 
\end{equation*}
We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. We know that, $S_{a,b}(T_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{T_p}$. Therefore
\begin{equation*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \neq S_{a,b}(0).
\end{equation*}
Then convexity adjustment for a CMS will be define as
\begin{equation}
CA_{CMS}(T_p) = \mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) - S_{a,b}(0).
\end{equation} 
Now, after some changes of measure, it is easy to show that
\begin{equation}\label{expected_t_p_cms}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) = \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
\end{equation}
where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$. Now ¡, if we apply Clark-Ocone formula to $S_{a,b}(T_a)$ and $M(T_a,T_p)$ we get
\begin{align} \label{clark_ocone_swap_m}
S_{a,b}(T_a) &= S_{a,b}(0) + \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s S_{a,b}(T_a) \right) dW^{01}_s  \nonumber \\
M(T_a,T_p) &= M(0,T_p)+ \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s M(T_a,T_p)\right) dW^{01}_s
\end{align}
Then, if we sustitute the last expressions in (\ref{expected_t_p_cms}) we have that
\begin{align}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} \mathbb{E}^{01}_{s}\left(\partial_x S_{a,b}(T_a)  D_s x_{T_a} \right)
\mathbb{E}^{01}_{s}\left(\partial_x M(T_a,T_p)  D_s x_{T_a} \right) ds \right) \nonumber \\
&= S_{a,b}(0) + \frac{\partial_x S_{a,b}(0)\partial_x M(0,T_p)}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a}  \left(\mathbb{E}^{01}\left(D_s x_{T_a}\right)\right)^{2}
 ds\right) \nonumber \\
&+ \cdots
\end{align}

\begin{example}
In the case of a Hull-White model, we showed  in 
$$
D_s x_{T_a} = \sigma \exp(-(T_a - s))
$$
and therefore, we have that
\begin{equation*}
\mathbb{E}^{\mathbb{Q}^{01}}\left(\int_{0}^{T_a}(D_s x_{T_a})^{2} ds \right) = \sigma^{2} \frac{1 - \exp(-2kT_a)}{2k}.
\end{equation*}

In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the last approximation and Monte Carlo method

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.3]{Figures/cms_convexity_order_1.jpg}
		\caption{Convexity Mc Vs Convexity Malliavin}
	\end{center}
\end{figure}

\section*{Appendix}
\appendix
\renewcommand{\thesection}{\Alph{section}.\arabic{section}}
\section{Approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$}
\label{expected_forward_measure_malliavin_derivative_x_t}
From (\ref{short_rate_cheyette}) is easy to show that
\begin{equation*}
x_{T_a} = \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) y_u du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x_u,y_u) dW_u^{\mathbb{Q}}  
\end{equation*}
In order to get an approximation for $D_sX_{T_a}$ we must to avoid the recurrence in the Malliavin derivative of $X_{T_a}$. Follow, the ideas of Piterbarg Volume II, we can approximate $y_t$ the next way
\begin{equation*}
y_t \approx \int_{0}^{t} \exp\left(-2\int_{u}^{t} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0) du
\end{equation*}
Therefore, if we define $\bar{y}(t)= \int_{0}^{s} \exp\left(-2\int_{u}^{s} k_{u^{\prime}} du^{\prime} \right) \eta(u,x_0,y_0)$, we have that
\begin{equation}\label{approximation_x_t_a}
X_{T_a} \approx \bar{X}(T_a):= \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}(u) du + \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}  
\end{equation}
With initial condition  $\bar{x}_{0}$ is such that $S_{a,b}(0,\bar{x}_0, \bar{y}({T_a})) = S_{a,b}(0)$ (see Piterbarg Volume II). Now, we must remember that by Girsanov's theorem we have that 
\begin{equation*}
dW^{\mathbb{Q}^{T_p}} = dW^{\mathbb{Q}} + \bar{\nu}(t,T_p) dt 
\end{equation*}
where $\bar{\nu}(t,T_p) = \int_{t}^{T_p} \eta(s,\bar{x}_s,\bar{y}_s) ds $. Then, we have the next approximation of $\bar{x}_{T_a}$
\begin{align*}
X_{T_a} &\approx \bar{x}_0  + \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{y}_s ds - \int_{0}^{T_a} \exp\left(-\int_{s}^{T_a}k_u du\right) \bar{\nu}(s, T_p) \eta(s,\bar{x}_s,\bar{y}_s) ds +  \\
&+ \int_{0}^{T_a}  \exp\left(-\int_{s}^{T_a}k_u du \right) \partial_x \eta(s,\bar{x}_s,\bar{y}_s) dW_s^{\mathbb{Q}}  
\end{align*} 
Therefore, if we taj¡ke the Malliavin derivative of $\bar{X}_{T_a}$ we get
\begin{equation}\label{approximation_D_s_x_t}
D_sX_{T_a} \approx  \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(s,\bar{x}_0,\bar{y}_{T_a})\bar{M}(s,T_a)
\end{equation}
where
\begin{align*}
\bar{M}(s,T_a) &= \exp\left(-\int_{s}^{T_a} \left( \frac{\left(\partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a})\right)^{2}}{2} - \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x (\bar{\nu}(u,T_a) \bar{\nu}(u,T_p))\right) du \right) \\ 
&\cdot\exp\left(\int_{s}^{t_0} \partial_x \beta(u,T_a,\bar{x}_0,\bar{y}_{T_a}) dW^{\mathbb{Q}}_u \right)
\end{align*}
With $\beta(u,T_a,x,y) = \exp\left(-\int_{u}^{T_a}k_u du\right) \partial_x \eta(u,x,y)$. Therefore, if we use the last equalities, we get the next approximation of $\mathbb{E}_s^{T_p}\left(D_s x_{T_a}\right)$

@@

\section{Approximation of $\mathbb{E}^{01}\left(x_t\right)$ and $\mathbb{E}^{01}\left(\left(x_t -\mathbb{E}^{01}\left(x_t\right)\right)^{2}\right)$}
It is easy to show that the dynamic of the bond under HJM assumption is
\begin{equation}
\frac{dP(t,T)}{P(t,T)} = r_t dt - \nu(t,T)dW^{\mathbb{Q}}_t.  
\end{equation}
Therefore, if we apply Itô formula we have that 
\begin{equation}\label{annuity_spot_dynamic}
\frac{d01(t,T_a,T_b)}{01(t,T_a,T_b)} = r_t dt - \sigma_{01}(t,T_a,T_b)dW^{\mathbb{Q}}_t
\end{equation}
where 
\begin{equation} \label{annuity_vol}
\sigma_{01}(t,T_a,T_b) = \frac{\sum_{i=a+1}^{b} \delta_{i-1,i} P(t,T_i) \nu(t,T_i)}{01(t,T_a,T_b)}.
\end{equation}
From (\ref{annuity_spot_dynamic}) and using the Girsanov's theorem that 
\begin{equation*}
dW^{01}_t = dW^{\mathbb{Q}}_t - \sigma_{01}(t,T_a,T_b)dt. 
\end{equation*}
We will use the last equation to get an approximation of the mean and order two moment of $x_t$. We can do the next approximaition of  (\ref{annuity_vol})
\begin{equation}
\sigma_{01}(t,T_a,T_b) \approx \sum_{i=a+1}^{b} w_i \nu(t,T_i)
\end{equation}
with $w_i=\frac{\delta_{i-1,i} P(0,T_i)}{01(0,T_a,T_b)}$. Now, if we use (\ref{short_rate_cheyette}) and the last approximation we have that
\begin{align}
x_t &\approx \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t}  \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}} \nonumber \\
&=  \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \sigma_{01}(u, T_a, T_b) du  + \nonumber \\ 
& \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{01} 
\end{align}
Therefore, we have that
\begin{align}
\mathbb{E}^{01}\left(x_t\right) &\approx \bar{x}_0  + \int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du\right) \bar{y}(u) du + \nonumber \\ &\int_{0}^{t} \exp\left(-\int_{s}^{t}k_u du \right) \eta(u,\bar{x}(u),\bar{y}(u)) \sigma_{01}(u, T_a, T_b) du \nonumber \\
\mathbb{E}^{01}\left(\left(x_t -\mathbb{E}^{01}\left(x_t\right)\right)^{2}\right) &\approx \int_{0}^{t} \exp\left(- 2 \int_{s}^{t}k_u du \right) \eta^{2}(u,\bar{x}(u),\bar{y}(u)) du
\end{align}
